\clearpage
{\small
\begin{thebibliography}{99}

\bibitem[He et al.(2020)]{he2020}
Xiangnan He, Kuan Deng, Xiang Wang, Yan Li, Yongdong Zhang, and Meng Wang.
\newblock LightGCN: Simplifying and powering graph convolution network for recommendation.
\newblock \emph{SIGIR}, 2020.
\newblock \url{https://arxiv.org/abs/2002.02126}

\bibitem[Kim et al.(2022)]{kim2022}
Minseok Kim, Jinoh Oh, Jaeyoung Do, and Sungjin Lee.
\newblock Debiasing neighbor aggregation for graph neural network in recommender systems.
\newblock \emph{CIKM}, 2022.
\newblock \url{https://arxiv.org/abs/2208.08847}

\bibitem[Kaggle mirror(2025)]{yahoor3kaggle}
Kaggle dataset mirror.
\newblock Yahoo!R3.
\newblock \url{https://www.kaggle.com/datasets/limitiao/yahoor3/data}

\bibitem[Li et al.(2023)]{li2023}
Haoxuan Li, Kunhan Wu, Chunyuan Zheng, Yanghao Xiao, Hao Wang, Zhi Geng, Fuli Feng, Xiangnan He, and Peng Wu.
\newblock Removing hidden confounding in recommendation: A unified multi-task learning approach.
\newblock \emph{NeurIPS}, 2023.

\bibitem[Li et al.(2024)]{li2024}
Haoxuan Li, Chunyuan Zheng, Sihao Ding, Peng Wu, Zhi Geng, Fuli Feng, and Xiangnan He.
\newblock Be aware of the neighborhood effect: Modeling selection bias under interference.
\newblock \emph{ICLR}, 2024.

\bibitem[Marlin and Zemel(2009)]{marlin2009}
Benjamin M.\ Marlin and Richard S.\ Zemel.
\newblock Collaborative prediction and ranking with non-random missing data.
\newblock \emph{RecSys}, 2009.

\bibitem[Schnabel et al.(2016)]{schnabel2016}
Tobias Schnabel, Adith Swaminathan, Ashudeep Singh, Navin Chandak, and Thorsten Joachims.
\newblock Recommendations as treatments: Debiasing learning and evaluation.
\newblock \emph{ICML}, 2016.
\newblock \url{https://proceedings.mlr.press/v48/schnabel16.html}

\bibitem[Steck(2010)]{steck2010}
Harald Steck.
\newblock Training and testing of recommender systems on data missing not at random.
\newblock \emph{KDD}, 2010.

\bibitem[Wang et al.(2019)]{wang2019}
Xiang Wang, Xiangnan He, Meng Wang, Fuli Feng, and Tat-Seng Chua.
\newblock Neural graph collaborative filtering.
\newblock \emph{SIGIR}, 2019.

\bibitem[Wang et al.(2020)]{wang2020}
Yixin Wang, Dawen Liang, Laurent Charlin, and David M.\ Blei.
\newblock Causal inference for recommender systems.
\newblock \emph{RecSys}, 2020.
\newblock \url{https://www.cs.columbia.edu/~blei/papers/WangLiangCharlinBlei2020.pdf}

\bibitem[Ying et al.(2018)]{ying2018}
Rex Ying, Ruining He, Kaifeng Chen, Pong Eksombatchai, William L.\ Hamilton, and Jure Leskovec.
\newblock Graph convolutional neural networks for web-scale recommender systems.
\newblock \emph{KDD}, 2018.

\bibitem[Yu et al.(2022)]{yu2022}
Junliang Yu, Hongzhi Yin, Xin Xia, Tong Chen, Lizhen Cui, and Quoc Viet Hung Nguyen.
\newblock Are graph augmentations necessary? Simple graph contrastive learning for recommendation.
\newblock \emph{SIGIR}, 2022.

\bibitem[Zhang et al.(2023)]{zhang2023}
Qing Zhang, Xiaoying Zhang, Yang Liu, Hongning Wang, Min Gao, Jiheng Zhang, and Ruocheng Guo.
\newblock Debiasing recommendation by learning identifiable latent confounders.
\newblock 2023.
\newblock \url{https://arxiv.org/abs/2302.05052}

\bibitem[Zhang et al.(2024)]{zhang2024}
An Zhang, Wenchang Ma, Pengbo Wei, Leheng Sheng, and Xiang Wang.
\newblock General debiasing for graph-based collaborative filtering via adversarial graph dropout.
\newblock \emph{WWW}, 2024.

\end{thebibliography}
}
